Thank You, Next

### 2022-06-28 Manuscript/manuscript_draft.tex
Update manuscript_draft.tex

\tom{Understanding interspecific mutualisms is a challenge, because they are among the most widespread species interactions with diverse and dynamic consequences.}{This sentence is pretty vague and does not have much information content.} 
Depending on environmental context the outcome of the interaction can range from parasitic to mutualistic. 
Most studies focus on a pair of species interacting in a mutualism, \tom{however often this is a simplification of the reality}{awkward and unclear -- pairs are ``real'' after all}. 
These mutualistic interactions \tom{become even more complex}{more complex than what?} when put into the context of a multi-species mutualism, where there are multiple partners interacting with the same focal species. 
The partners can directly impact the focal species through the interactions, \tom{and indirectly impact them through interactions with each other}{This is true but not something we are well poised to address with our data so might be risky to bring it up.}. 
The cactus \textit{Cylindriopuntia imbricata} forms \tom{symbioses}{technically it's not a symbiosis because the partners live independently} with multiple ant species, but each individual plant is able to \tom{interact}{This sentence does not sufficiently convey the nature of the interaction - the plants reward ants with extrafloral nectar in exchange for defense} with \tom{only one species at a time}{There is not enough context to know why this information is relevant here. Abstracts should be brutally efficient in communicating the essentials.}. 
Using \tom{a long-term data-set}{This should be unpacked a bit more. How long, where, what type of data?}, we show that there are differences in the \tom{impacts of different ant partners}{How many partners?} on \tom{various vital rates of the cacti across ontogeny}{This sounds a little nebulous, be more specific.}.
Our results demonstrate the importance of evaluating a mutualism within a community context and \tom{suggest that even slight differences of rewards between mutualist partners can help promote fitness of the cacti}{Nothing you have reported in the abstract so far really supports this statement.}.

@@

\section*{Context/Introduction}
\subsection*{Context}
\tom{}{The Intro section should generally not have subsections.}
Mutualisms are species interactions in which all involved participants benefit. They are among the most widespread species interactions\cite{Chamberlain2014,Stachowicz2005,BoucherDouglasH.1985} with diverse and dynamic consequences, \tom{yet they are still poorly understood}{What, specifically, is poorly understood?}. 
\tom{They form a complex foundation to many natural systems}{Not sure what this means} \tom{which involve both costs and benefits, despite their nature of being beneficial.}{I get what you are trying to say here but the phrasing is a little awkward, could be sharpened.}

\tom{There are benefits of mutualistic interactions, but there are costs as well}{redundant with last sentence of previous paragraph}, some direct and some indirect. \tom{}{This topic sentence does not effectively build on the multi-species emphasis of the previous paragraph.}
Directly, mutualistic partners can sometimes become parasitic, causing harm to the focal mutualist\cite{Bronstein2001a}. 
\tom{More indirectly, these interactions require energy.}{Awkward sentence, and I'm not sure why investment is reward is an indirect cost.} 
\tom{Within a mutualism, each participant offers rewards and in return receives benefits from their partners.}{No new information content in this sentence.} 
These rewards come in many forms (nectar, protection, habitat, etc.), all of which require some investment \cite{Bronstein2001}. 
These investments can be seen as the costs of mutualisms, they are traded for the rewards provided by a partner. 
\tom{Because of these trade-offs}{trade-offs between what and what?}, there are both costs and benefits to a mutualistic interaction\cite{Bronstein2001,Bronstein2001a}, \tom{particularly as the mutualism becomes more complex in the context of its environment}{I don't know what this means.}.\tom{}{Having made it to the end of this paragraph I can't really find any new information here. You are covering very basic aspects of mutualism that were already described in the first paragraph. I would get to the question/problem at the core of this paper more quickly.}

>>>>

Mutuaisms are among the most widespread species interactions with diverse and dynamic consequences.
Depending on environmental context the outcome of the interaction can range from parasitic to mutualistic. 
Most studies focus on a pair of species interacting in a mutualism, however most observed mutualistic interactions include more than two species. 
These are multi-species mutualisms, where there are multiple partners interacting with the same focal species. 
\hl{The partners can directly impact the focal species through the interactions, \tom{and indirectly impact them through interactions with each other}{***This is true but not something we are well poised to address with our data so might be risky to bring it up.***}. }
The cactus \textit{Cylindriopuntia imbricata} reward partners with extrafloral nectar in exchange for defense by various ant species (primarily \textit{Crematogaster opuntiae} and \textit{Liometopum apiculatum}, though there are many other ant species with smaller populations) from herbivores and seed predators. 
\hl{Using a 20-year collection of demographic data (growth, survival, reproduction, ant partners, herbivory, etc.) from these cacti in New Mexico, we estimate the fitness of the cacti populations with every combination of partners, allowing us to *** understand what accounts for partner diversity in this system *** understand if the current partner diversity of the system is associated with the optimal fitness *** and the impacts of these partners on different vital plant processes across their life history (such as partner impacts on reproduction, survival, or growth). }
We found that different ant partners had different impacts on cacti vital rates suggesting there may be a different 'best' partner during pre-reprodctive life stages than during reproductive life stages, and that the highest cacti fitness is associated with the current partner set (all possible ant partners are available).
Together, these results suggest that complementarity may account for the benefits that these plants experience with partner diversity. 
Our results demonstrate the importance of evaluating a mutualism within a community context and \tom{suggest that even slight differences of rewards between mutualist partners can help promote fitness of the cacti}{Nothing you have reported in the abstract so far really supports this statement.}.

@@

\section*{Context/Introduction}
BASELINE OF MUTUALISMS
Mutualisms are species interactions in which all involved participants benefit. They are among the most widespread species interactions\cite{Chamberlain2014,Stachowicz2005,BoucherDouglasH.1985} with diverse and dynamic consequences.

PAIRWISE VS MULTISPECIES

There are benefits of mutualistic interactions, but there are costs as well, some direct and some indirect. 
Directly, mutualistic partners can sometimes become parasitic, causing harm to the focal mutualist\cite{Bronstein2001a}. 
\tom{More indirectly, these interactions require energy.}{Awkward sentence, and I'm not sure why investment is reward is an indirect cost.} 
\tom{Within a mutualism, each participant offers rewards and in return receives benefits from their partners.}{No new information content in this sentence.} 
These rewards come in many forms (nectar, protection, habitat, etc.), all of which require some investment \cite{Bronstein2001}. 
These investments can be seen as the costs of mutualisms, they are traded for the rewards provided by a partner. 
\tom{Because of these trade-offs}{trade-offs between what and what?}, there are both costs and benefits to a mutualistic interaction\cite{Bronstein2001,Bronstein2001a}, \tom{particularly as the mutualism becomes more complex in the context of its environment}{I don't know what this means.}.\tom{}{Having made it to the end of this paragraph I can't really find any new information here. You are covering very basic aspects of mutualism that were already described in the first paragraph. I would get to the question/problem at the core of this paper more quickly.}
